---
title: "About"
description: | 
  Hi, I'm Alex. I was born and raised in the Philippines. I lived there until I was 15 when I migrated to the United States with my mother and sister as permanent residents. I became a U.S. citizen in 2017. I am an amateur artist, and my hobbies include painting, drawing, and playing video games. I also like cooking, eating, and traveling.
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source(file.path("R", "functions.R"))
```

## Education

* **Ph.D. in Applied Mathematics** | University of California Merced | 2021

  My dissertation explored the use of mathematical models to study the evolution of natural language. My dissertation was titled "Mathematical Models of Natural Language Evolution."
  
  In my dissertation, I focused on three main areas:
  
    - Modeling word rank evolution: I developed a mathematical model to predict how the frequency of words changes over time.
    - Exploring the evolution of contextual semantics: I investigated how the meaning of words changes depending on the context in which they are used.
    - Evaluating the accuracy of reading comprehension tasks: I used machine learning to fine-tune a pre-trained language model to predict whether a human will correctly answer a reading comprehension question.
  
* **B.S. in Mathematics** | East Tennessee State University | 2015
  
  My undergraduate "thesis" was about stochastic modeling of spider predation movements.

There are more details about me on my Curriculum Vitae.

```{r, echo=FALSE}
icon_link(
    text = "CV",
    url  = "https://drive.google.com/file/d/1EdgKNWkFlHiBBEBRDDoaNq1Nw4S4IjmR/view?usp=sharing"
)
```

<br />

## Research

I am interested in the mathematical applications of data science in interdisciplinary research, particularly the mathematical modeling of natural languages, social and biological systems. I am also interested in generating insights from data to inform researchers in evolutionary linguistics, sociology, mathematical biology, and decision-makers in social justice initiatives.

[Read More...](Research.html)

<br />

## Teaching

I am an Assistant Professor of Mathematics at the University of Portland. I primarily teach courses in calculus, ordinary differential equations, probability and statistics, applied statistics, and data science. In my courses I apply (a) student-centered learning by using a variety of instructional methods to engage students, (b) inclusive classroom by creating a safe and welcoming environment, and (c) diversified grading systems and teaching tools, such as think-pair-share activities, proficiency-based grading systems, and group work.

[Read More...](teaching.html)

<br />

## Recent Activities

<style type="text/css">
.tg  {border-collapse:collapse;border-color:#9ABAD9;border-spacing:0;}
.tg td{background-color:#EBF5FF;border-color:#9ABAD9;border-style:solid;border-width:1px;color:#444;
  font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;word-break:normal;}
.tg th{background-color:#409cff;border-color:#9ABAD9;border-style:solid;border-width:1px;color:#fff;
  font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;word-break:normal;}
.tg .tg-7ods{background-color:#efefef;border-color:#002b36;color:#002b36;text-align:left;vertical-align:top}
.tg .tg-zlo5{background-color:#efefef;border-color:#002b36;color:#002b36;font-weight:bold;text-align:right;vertical-align:top}
.tg .tg-5rib{background-color:#efefef;border-color:#002b36;color:#002b36;text-align:left;vertical-align:top}
.tg .tg-f7xd{background-color:#efefef;border-color:#002b36;color:#002b36;font-weight:bold;text-align:left;vertical-align:top}
.tg .tg-pgs2{background-color:#efefef;border-color:#002b36;color:#002b36;font-weight:bold;text-align:center;vertical-align:top}
.tg .tg-3b1p{background-color:#efefef;border-color:#002b36;color:#002b36;font-weight:bold;text-align:center;vertical-align:top}
.tg .tg-skp8{background-color:#efefef;border-color:#002b36;color:#002b36;font-weight:bold;text-align:right;vertical-align:top}
.tg .tg-vreo{background-color:#efefef;border-color:#002b36;color:#002b36;font-weight:bold;text-align:left;vertical-align:top}
</style>
<table class="tg">
<thead>
  <tr>
    <th class="tg-3b1p">2023</th>
    <th class="tg-skp8">May 29 - August 7</th>
    <th class="tg-7ods">* I led a SURE-funded collaborative project with two undergraduate students, where we visualized the data and created a system of differential equations to model it.</th>
  </tr>
</thead>
<tbody>
  <tr>
    <td class="tg-pgs2">2022</td>
    <td class="tg-zlo5">November 19</td>
    <td class="tg-5rib">* I was awarded with the University of Portland Butine Conference fund to attend the 2023 Joint Mathematics Meetings conference as part of my MAA Project NExT activities.</td>
  </tr>
  <tr>
    <td class="tg-3b1p"></td>
    <td class="tg-skp8">June 6 - August 12</td>
    <td class="tg-7ods">* An undergraduate student conducted a SJRE-funded project under my supervision, in collaboration with me, using exploratory data analysis and Poisson regression.</td>
  </tr>
  <tr>
    <td class="tg-pgs2">2021</td>
    <td class="tg-zlo5">December 1</td>
    <td class="tg-5rib">* I was selected to be an MAA Project NExT Fellow for Red'22 Cohort.</td>
  </tr>
  <tr>
    <td class="tg-3b1p"></td>
    <td class="tg-skp8">June 15</td>
    <td class="tg-7ods">* I presented my poster titled "Evolving Contextual Semantics" at the Virtual SMB 2021 Annual Meeting.</td>
  </tr>
  <tr>
    <td class="tg-pgs2"></td>
    <td class="tg-zlo5">May 10</td>
    <td class="tg-5rib">* I successfully defended my dissertation titled "Mathematical Models of Natural Language Evolution".</td>
  </tr>
  <tr>
    <td class="tg-3b1p">2020</td>
    <td class="tg-skp8">June 8 - August 14</td>
    <td class="tg-7ods">* I finished the machine learning internship funded by the Computational Engineering Department at the Lawrence Livermore National Laboratory.</td>
  </tr>
  <tr>
    <td class="tg-pgs2"></td>
    <td class="tg-zlo5">August 6</td>
    <td class="tg-5rib">* I presented my talk titled "Word Embedding Models Performance Analysis on a Question Answering Task" at the Virtual Lawrence Livermore National Laboratory Summer Student SLAM.</td>
  </tr>
  <tr>
    <td class="tg-3b1p">2019</td>
    <td class="tg-skp8">May 20 - August 16</td>
    <td class="tg-7ods">* I finished the Data Science Summer Institute (DSSI) internship funded by the Center for Applied Scientific Computing at the Lawrence Livermore National Laboratory.</td>
  </tr>
  <tr>
    <td class="tg-vreo"></td>
    <td class="tg-zlo5">August 8</td>
    <td class="tg-5rib">* I presented my poster titled "Application of Convolutional Neural Network on Radiative Opacity Computations" at the Lawrence Livermore National Laboratory Poster Symposium.<br></td>
  </tr>
  <tr>
    <td class="tg-f7xd"></td>
    <td class="tg-skp8">July 15</td>
    <td class="tg-7ods">* I presented my talk titled "Data Science Tools and Techniques with Applications in Natural Language Processing" at the Virtual 2nd Joint SIAM/CAIMS Annual Meeting.</td>
  </tr>
</tbody>
</table>
