---
title: "About"
description: | 
  Hi, I'm Alex. I was born and raised in the Philippines. I lived there until I was 15 when I migrated to the United States with my mother and sister as permanent residents. I became a U.S. citizen in 2017. I am an amateur artist, and my hobbies include painting, drawing, and playing video games. I also like cooking, eating, and traveling.
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source(file.path("R", "functions.R"))
```

## Education

* **Ph.D. in Applied Mathematics** | University of California Merced | 2021

  My dissertation explored the use of mathematical models to study the evolution of natural language. My dissertation was titled "Mathematical Models of Natural Language Evolution."
  
  In my dissertation, I focused on three main areas:
  
    - Modeling word rank evolution: I developed a mathematical model to predict how the frequency of words changes over time.
    - Exploring the evolution of contextual semantics: I investigated how the meaning of words changes depending on the context in which they are used.
    - Evaluating the accuracy of reading comprehension tasks: I used machine learning to fine-tune a pre-trained language model to predict whether a human will correctly answer a reading comprehension question.
  
* **B.S. in Mathematics** | East Tennessee State University | 2015
  
  My undergraduate "thesis" was about stochastic modeling of spider predation movements.

There are more details about me on my Curriculum Vitae.

```{r, echo=FALSE}
icon_link(
    text = "CV",
    url  = "https://drive.google.com/file/d/1EdgKNWkFlHiBBEBRDDoaNq1Nw4S4IjmR/view?usp=sharing"
)
```

<br />

## Research

I am interested in the mathematical applications of data science in interdisciplinary research, particularly the mathematical modeling of natural languages, social and biological systems. I am also interested in generating insights from data to inform researchers in evolutionary linguistics, sociology, mathematical biology, and decision-makers in social justice initiatives.

[Read More...](Research.html)

<br />

## Teaching

I am an Assistant Professor of Mathematics at the University of Portland. I primarily teach courses in calculus, ordinary differential equations, probability and statistics, applied statistics, and data science. In my courses I apply (a) student-centered learning by using a variety of instructional methods to engage students, (b) inclusive classroom by creating a safe and welcoming environment, and (c) diversified grading systems and teaching tools, such as think-pair-share activities, proficiency-based grading systems, and group work.

[Read More...](teaching.html)
