---
title: "Teaching"
description: | 
  I teach undergraduate mathematics courses in the Department of Mathematics at the University of Portland.
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source(file.path("R", "functions.R"))
```

::: {.infobox data-latex="{caution}"}
::: {.center data-latex=""}
**Attention University of Portland Students!**

If you are here for the **Fall 2023** course materials of **Calculus I** or **Ordinary Differential Equations**, please visit the following links.

```{r, echo=FALSE}
icon_link(
    text = "MTH-201 (Calculus I)",
    url  = "https://upmathematics.github.io/mth-201e-fa23/"
)
```

```{r, echo=FALSE}
icon_link(
    text = "MTH-321 (Ordinary Differential Equation)",
    url  = "https://upmathematics.github.io/mth-321b-fa23/"
)
```
:::
:::

## Courses

### University of Portland

*These are subjects I taught as instructor.*

  - **MTH-201 (Calculus I)**
  
    *Semesters Taught:* [Fall 2023](https://upmathematics.github.io/mth-201e-fa23/){target="_blank"}
  
  - **MTH-202 (Calculus II)**
  
    *Semesters Taught:* [Spring 2023](https://upmathematics.github.io/mth-202a-sp23/){target="_blank"} | [Fall 2022](https://upmathematics.github.io/mth-202a-fa22/){target="_blank"}
  
  - **MTH-321 (Ordinary Differential Equations)**
  
    *Semesters Taught:* [Fall 2023](https://upmathematics.github.io/mth-321b-fa23/){target="_blank"}
  
  - **MTH-461 (Probability & Statistics)**
  
    *Semesters Taught:* [Fall 2022](https://upmathematics.github.io/mth-461a-fa22/){target="_blank"}
    
  - **MTH-361 (Applied Statistics)**
  
    *Semesters Taught:* [Spring 2023](https://upmathematics.github.io/mth-361ab-sp23/){target="_blank"}

### Reed College

*These are subjects I taught as instructor.*

  - **MATH-241 Data Science**
  
    *Semesters Taught:* [Spring 2022](https://reed-statistics.github.io/math241-spring2022/){target="_blank"}
    
  - **MATH-141 (Introduction to Probability & Statistics)**
  
    *Semesters Taught:* [Fall 2021](https://reed-statistics.github.io/math141-fall2021/){target="_blank"}

### University of California Merced

*These are subjects I taught as a teaching assistant.*

  - Probability and Statistics
  - Linear Algebra
  - Calculus
  - Vector Calculus
  - Differential Equations
  
## Teaching Philosophy

As a student, I learn best by understanding complex ideas through simple illustrations. I start with the big picture and then fill in the details later. This holistic perspective has helped me throughout my educational journey, and I believe it is essential for all students.

I think that there are three critical elements of education: student-centered learning, an inclusive classroom, and diversified grading systems and teaching tools.

  * *Student-centered learning* is important because it allows students to learn in a way that is most effective for them. I use a variety of instructional methods to engage students, such as group activities, worksheets, visualizations, and traditional lectures. I also provide detailed feedback and support so that students can reach their full potential.

  * An *inclusive classroom* is meaningful because it creates a safe and welcoming environment where all students feel welcome, respected, and supported. I create an inclusive classroom by using inclusive language, celebrating diversity, and being aware of and addressing bias.

  * *Diversified grading systems and teaching tools* are essential because they allow me to assess student learning in a fair and equitable way. I use a variety of grading methods and teaching tools, such as proficiency-based grading system, rubrics, portfolios, and self-assessment. This allows me to assess student learning in a way that is tailored to each student's individual needs.
